%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% I, the copyright holder of this work, release this work into the
%% public domain. This applies worldwide. In some countries this may
%% not be legally possible; if so: I grant anyone the right to use
%% this work for any purpose, without any conditions, unless such
%% conditions are required by law.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[
  digital,     %% The `digital` option enables the default options for the
               %% digital version of a document. Replace with `printed`
               %% to enable the default options for the printed version
               %% of a document.
%%  color,       %% Uncomment these lines (by removing the %% at the
%%               %% beginning) to use color in the printed version of your
%%               %% document
  oneside,     %% The `oneside` option enables one-sided typesetting,
               %% which is preferred if you are only going to submit a
               %% digital version of your thesis. Replace with `twoside`
               %% for double-sided typesetting if you are planning to
               %% also print your thesis. For double-sided typesetting,
               %% use at least 120 g/m² paper to prevent show-through.
  nosansbold,  %% The `nosansbold` option prevents the use of the
               %% sans-serif type face for bold text. Replace with
               %% `sansbold` to use sans-serif type face for bold text.
  nocolorbold, %% The `nocolorbold` option disables the usage of the
               %% blue color for bold text, instead using black. Replace
               %% with `colorbold` to use blue for bold text.
  nolof,         %% The `lof` option prints the List of Figures. Replace
               %% with `nolof` to hide the List of Figures.
               %% TODO: maybe show LoF
  nolot,         %% The `lot` option prints the List of Tables. Replace
               %% with `nolot` to hide the List of Tables.
               %% TODO: maybe show LoT
]{fithesis4}
%% The following section sets up the locales used in the thesis.
\usepackage[resetfonts]{cmap} %% We need to load the T2A font encoding
\usepackage[T1,T2A]{fontenc}  %% to use the Cyrillic fonts with Russian texts.
\usepackage[
  main=english, %% By using `czech` or `slovak` as the main locale
                %% instead of `english`, you can typeset the thesis
                %% in either Czech or Slovak, respectively.
  english, german, czech, slovak %% The additional keys allow
]{babel}        %% foreign texts to be typeset as follows:
%%
%%   \begin{otherlanguage}{german}  ... \end{otherlanguage}
%%   \begin{otherlanguage}{czech}   ... \end{otherlanguage}
%%   \begin{otherlanguage}{slovak}  ... \end{otherlanguage}
%%
%%
%% The following section sets up the metadata of the thesis.
\thesissetup{
    date        = \the\year/\the\month/\the\day,
    university  = mu,
    faculty     = fi,
    type        = mgr,
    department  = Software Engineering,
    author      = Adam Krídl,
    gender      = m,
    advisor     = {RNDr. Adam Rambousek, Ph.D.},
    title       = {Enhancement of Clusterability and Maintainability of Repour Service},
    TeXtitle    = {Enhancement of Clusterability and Maintainability of Repour Service},
    keywords    = {Red Hat, microservices, Quarkus, build system},
    TeXkeywords = {Red Hat, microservices, Quarkus, build system},
    abstract    = {%
        This thesis was created as an effort of Red Hat's Project Newcastle to migrate an existing microservice Repour from Python to Quarkus, and enhance some of key cloud-native properties, namely clusterability and maintainability.

        As part of the thesis, such a solution was designed and implemented, improving the current solution. The new solution is prepared to be fully migrated once Project Newcastle decides to do so.
    },
    thanks      = {%
        Firstly, I would like to thank my advisor RNDr. Adam Rambousek, Ph.D. for his time, support, and all the helpful advices he had provided me.

        Secondly, I would like to thank my army of official and unofficial consultants — my colleagues at work — without who I would have no chance to manage the thesis in time: Dustin, who helped me mainly with understanding of Repour internals. Ján, for helping me to get into MPP deployments. Jožo, for helping me to get into OCP-C1 deployments. Yet the biggest thanks belongs to Honza, who always patiently went through thousands of lines of code during PRs, endless discussions regarding high-level design, and generally, being such a tremendous mentor during all my internship period.

        Thirdly, I have to thank Kuba for helping me to find such a suitable thesis, providing me all the time required to work on it, and giving me the opportunity to learn plenty of new stuff during this time.

        Last but not least, I would like to thank my family who supported me during the whole time of my studies, it would not be possible without you.
    },
    bib         = bibliography.bib,
    %% Remove the following line to use the JVS 2018 faculty logo.
    facultyLogo = fithesis-fi,
}
\usepackage{makeidx}      %% The `makeidx` package contains
\makeindex                %% helper commands for index typesetting.
%% These additional packages are used within the document:
\usepackage{paralist} %% Compact list environments
\usepackage{amsmath}  %% Mathematics
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage[hyphens]{url}      %% Hyperlinks
\usepackage{markdown} %% Lightweight markup
\usepackage{listings} %% Source code highlighting
\lstset{
  basicstyle      = \ttfamily,
  identifierstyle = \color{black},
  keywordstyle    = \color{blue},
  keywordstyle    = {[2]\color{cyan}},
  keywordstyle    = {[3]\color{olive}},
  stringstyle     = \color{teal},
  commentstyle    = \itshape\color{magenta},
  numbers         = left,
  numbersep       = 5pt,
  breaklines      = true,
}
\usepackage{floatrow} %% Putting captions above tables
\floatsetup[table]{capposition=top}
\usepackage[babel]{csquotes} %% Context-sensitive quotation marks
\usepackage[perpage]{footmisc}
\usepackage{subfiles}  %% Allows multi-file project
\usepackage{hyperref}  %% Alows using \href

\begin{document}

\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction} %% Add the (unnumbered) chapter introduction into the ToC, since unnumbered chapters are not added there implicitly
\label{chap:introduction}
\subfile{chapters/introduction/main}

\chapter{Context}
\label{chap:context}
\subfile{chapters/context/main}

\chapter{Repour microservice}
\label{chap:repour}
\subfile{chapters/repour/main}

\chapter{Reqour microservice}
\label{chap:reqour}
\subfile{chapters/reqour/main}

\chapter{Comparision of Repour and Reqour}
\label{chap:comparision}
\subfile{chapters/comparision/main}

\chapter{Deployment}
\label{chap:deployment}
\subfile{chapters/deployment/main}

\chapter*{Conclusion}
\label{chap:conclusion}
\subfile{chapters/conclusion/main}

%% Appendices
\subfile{appendix/main}

\end{document}
